\chapter{Minimum-Violation Planning for Urban Air Mobility}
In general, it is not always feasible to guarantee the satisfaction of all safety constraints under all conditions. Such scenarios are explicitly accounted for in 14 CFR \S 107.21, which allows for emergency deviation from regulations if required as long as the deviation is reported. For example, a vehicle may have to make an emergency landing if it is about to run out of fuel, even if violates separation requirements. Thus, there is a need for an air traffic management approach that allows for \emph{formally justifiable} violation of safety constraints if necessary. The following presents our work on the synthesis of control strategies for automated air traffic management for UAM while obeying safety regulations. In particular, we focus on the case where all safety regulations cannot be feasibly satisfied, which is allowed for small, cargo-carrying UAS under emergency operation. We present a decentralized, scalable synthesis approach that provably \emph{minimally violates} the given safety requirements.  Note that if it is possible to satisfy all safety properties for the duration of the flight, the approach yields a solution with zero violations (i.e., all safety requirements are guaranteed for the duration of the flight). 

Our approach is based on minimum-violation planning for systems that are subject to potentially infeasible safety requirements. Given a prioritized safety specification, which specifies the priority and weight of each safety requirement, minimum-violation planning computes a plan that minimally violates the requirements. In particular, we propose a novel \emph{decentralized approach} to minimum-violation planning in order to handle large-scale systems that cannot be handled by current state-of-the-art approaches. 

%\input{UAM-NFM/01_Intro}
%
\input{UAM-NFM/02_Background}
%%
\input{UAM-NFM/03_Problem}
%%
%\input{UAM-NFM/04_Solution}
%%
\input{UAM-NFM/05_Experiments}


