\section{Extension to trajectories of arbitrary length}

Previously, we assumed that the length of any trajectory is bound by some constant $\ell$. %If this $\ell$ is large, then the resultant graph constructed by the pathfinder also becomes large.
In this section, we define the problem for trajectories of arbitrary length and propose a solution. We show how to use the ordering mechanism to ensure that the enforcers can ensure safe behavior even when the trajectories are of arbitrary length. Formally, the problem is stated as: \\


Given a set $\Agents = \{u_1,\dots,u_n\}$ of agents and a set $\{(v_u,w_u)~|~u \in \Agents \}$ of their trajectories, 
construct a set $\{S[u,t]~|~u \in \Agents \text{ and } t \in \Time\}$ of enforcers such that these enforcers are correct, cause minimum deviation and bounded. 


Luckily, we do not have to change the entire synthesis procedure to solve this problem. We artificially restrict the input to the enforcers. Let $w_u(0)$ be the trajectory (possibly infinite) for agent $u$ and $v_u$ be the start state of the agent. 
We divide $w_u$ into blocks of length $\ell$, $w_u(0) =w_u[0:\ell-1]\cdot w_u[\ell:2\ell-1]\dots.$ The enforcer $S[u,0]$ uses $w_u(0)$ as its trajectory, once it reaches the final state $\hat{\delta}(v_u,w_u(0))$, it uses \begin{small}$\big( (\hat{\delta}(v_u,w_u(0)),  w_u[\ell:2\ell-1] \big)$ \end{small} as the new trajectory for the enforcer synthesis. Algorithm \ref{Trajectory_update} describes this procedure.

%This procedure is presented in Algorithm \ref{Trajectory_update}.

In the algorithm, whenever the agent reaches its final state, its trajectory is updated with the next $\ell$ moves and its flags are also suitably reset. The correctness of this procedure is a direct consequence of the main theorem.


\begin{algorithm}
\KwResult{Trajectory of length at most length $\ell+k$}
$i=0$\;
Initialize $w_u$ and $v_u$\;
$v_u^f = \hat{\delta}(v_u,w_u(0)[0:\ell])$\;
$w_u(0) = w_u[0:\ell]$\;
\While{True}{
Update Communication Groups \;
Increment Time \;
\If{$goal_{u,t} = \top$}{
$i++$\;
$v' = v_u^f$\;
$w_u(t) = w_u[i\ell:(i+1)\ell]$\;
$v_u^f = \hat{\delta}(v_u,w_u[i\ell:(i+1)\ell-1])$\;
$v_u = v'$\;
}
\ForAll{$v$ in $\Agents_u$}{
\If{($u$, $v$ violate safety) $\land (v =_{t} u)$}
{
    \If{$v \prec_{0} u$}{Call the pathfinder on $u$ and find a new path \;} 
}
\ElseIf{($u$, $v$ violate safety) $\land (v \prec_{t} u)$}
{
    Call the pathfinder on $u$ and find a new path \;
    $B_u = \emptyset$ \;
}
}
t++ \;
}
\caption{Enforcer on agent $u$.}
\label{Trajectory_update}
\end{algorithm}

